### 2023-12-26 thesis/chapters/02-analysis-A-CdM.tex
Rough draft of vibration measurement plan
Vibration measurement plan

\subsection{Technical standards}
Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards. Standards are concerned with each step in the process that originates with transducer placements and data acquisition. They prescribe conventions for setting fault severity levels and provide empirically observed vibration characteristics of common defects. Relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
\bigbreak

@@

\emph{Zone A} is reserved for newly commissioned machines. \emph{Zone B} signifies suitability for long-term operation. In \emph{zone C} the machine is deemed in unsatisfactory condition and corrective action should be taken soon. Finally, in zone D vibrations can cause damage to the machine. The span of acceptable values differs with the machine class from I through to IV and their output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.

>>>>

\subsection{Technical standards} \label{section:technical-standards}
Vibration-based condition monitoring practices adopted in the factory's predictive maintenance management must comply with normative guidelines formalized in ISO international standards. Standards are concerned with each step in the process that originates with transducer placements and data acquisition. They prescribe conventions for setting fault severity levels and provide empirically observed vibration characteristics of common defects. Relevant standards for IoT diagnostics systems are \emph{ISO 20816} (updated from ISO 10816) and \emph{ISO 13373}.
\bigbreak

@@

\emph{Zone A} is reserved for newly commissioned machines. \emph{Zone B} signifies suitability for long-term operation. In \emph{zone C} the machine is deemed in unsatisfactory condition and corrective action should be taken soon. Finally, in \emph{zone D} vibrations can cause damage to the machine. The span of acceptable values differs with the machine class from I through to IV and their output power of 15~kW (class~I), 75~kW (class~II), 10~MW (class~III), or greater.

### 2023-12-26 thesis/chapters/03-design.tex
Vibration measurement plan

Confusion matrices for fault predicion and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}. In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree. The most inaccuracies in the temporal domain are between misalignment and bearing race faults. In the spectral domain, the model confuses imbalance and bearing faults. It is to be expected since mass to unbalance the shaft is hanged to simulate bearing defects.

@@

During gradual learning, the correct label is supplied after a fixed period passes after its prediction. This \textbf{sliding window} simulation examines accuracy every 100 iterations. Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{ffig:design:online-fault-delay-sliding}).

@@

\section{Vibration measurement plan}

\subsection{Machinery}
% Enum list

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=0.5\textwidth]{assets/design/machine-fan.jpg}
        \caption{Stand fan Kalorik}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=0.5\textwidth]{assets/design/machine-compressor.jpg}
        \caption{Scroll compressor Copeland}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
        \caption{Water pump KSB Omega}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
        \caption{Water pump Sigma}
    \end{subfigure}
    \caption{Machine}
\end{figure}

\subsection{Sensors}

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Accelerometers}
\end{table}

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{assets/design/hw-block-schematic.png}
	\caption{Sensor unit hardware block diagram}
\end{figure}

\subsection{Preliminary measurements}
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.44\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
        \caption{Temporal domain waveforms in all spatial directions with 300 ms duration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.55\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
        \caption{Spectral domain in x accelerometer axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
    \end{subfigure} 
    \caption{Signals at 5 s timestamp}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.6\textwidth]{assets/design/compressor-orbitals-1x.png}
	\caption{Orbital analysis of compressor's 1x harmonic}
\end{figure}

>>>>

Confusion matrices for fault prediction and high severity anomaly are shown in Figure \ref{fig:design:knn-confusion-matrix}. In this example, the number of k neighbors is 5, the distance metric is the Euclidian norm, and the algorithm for proximity queries is a k-d tree. The most inaccuracies in the temporal domain are between misalignment and bearing race faults. In the spectral domain, the model confuses imbalance and bearing faults because mass to unbalance is hung onto the shaft to cause bearing defects.

@@

During gradual learning, the correct label is supplied after a fixed period passes after its prediction. This \textbf{sliding window} simulation examines accuracy every 100 iterations. Wait times before revealing the actual class associated with the sample are 1, 50, 100, or 250 steps (Fig.~\ref{fig:design:online-fault-delay-sliding}).

@@

\section{Dataset collection in industrial environment}
The methodology applied so far for the dataset recorded in a laboratory is to be tested on vibration signals from the industrial environment. Established guidelines for introducing a monitoring system have been described in the section on technical standards (Section~\ref{section:technical-standards}). We employ a slightly customized validation procedure that involves the selection of machines to be monitored, identifying positions for measurements according to technical specifications, taking preliminary readings, and developing a device capable of capturing the usual failure modes. The collection of the novel dataset is accompanied by an agreed upon schedule.

\subsection{Machinery}
Three kinds of rotating machines are at disposal for vibration measurements. Those are a standing fan, scroll compressor, and water pump.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.17\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-fan.jpg}
        \caption{\footnotesize Fan}
        \label{fig:machine:fan}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.17\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-compressor.jpg}
        \caption{\footnotesize Compressor}
        \label{fig:machine:compressor}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-ksb-pump.jpg}
        \caption{\footnotesize Water pump KSB}
        \label{fig:machine:pump-ksb}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.31\textwidth}
    		\centering
        \includegraphics[width=\textwidth]{assets/design/machine-sigma-pump.jpg}
        \caption{\footnotesize Water pump Sigma}
        \label{fig:machine:pump-sigma}
    \end{subfigure}
    \caption{Machines dedicated for vibration measurements}
\end{figure}

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the sensor unit development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm). Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}) and altogether two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll. Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.

\textbf{Water pumps} are available as 3 units in municipal drinking water pumping station. The apparatus consists of a single-stage axially split volute casing pump and an attached electric induction motor with a squirrel cage rotor.

The newer primary pump with cloud monitoring solution is one unit of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pump was commissioned in 2019 and it rotates at a speed of circa 1500 rpm (precisely 1493 rpm or 24.9 Hz). The electric motor in the vicinity has 400~kW of power (class~\rom{2}). Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.

Secondary pumps are two units produced by \emph{Sigma} (Fig.~\ref{fig:machine:pump-sigma}) in 1986 with motor powers of 250~kW and 100~kW. Each pump and motor has 2 bearings therefore there are 4 measurement positions in total.

\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix \ref{appendix:data-collection}.

\subsection{Sensors}
In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller. The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate. Hardware parameters of previous and proposed sensor units are in Table~\ref{tab:design:hw-sensors}.

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55             & 5 - 6.3            \\ \hline
\textbf{Sensitivity}                             & 300 mV/g         & 0.061 mg/LSB       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Accelerometers}
\label{tab:design:hw-sensors}
\end{table}

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. An interface capable of higher speeds is needed to store all acceleration samples. Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pins. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.9\textwidth]{assets/design/hw-block-schematic.png}
	\caption{Sensor unit hardware block diagram}
	\label{fig:design:block-diagram-hw}
\end{figure}

The drivers for necessary low-level interfaces and FAT32 filesystem are  implemented already in ESP-IDF software development kit\footnote{ESP-IDF SDK: \url{https://docs.espressif.com/projects/esp-idf/en/latest/esp32/api-reference/index.html}}. The accelerometer driver is also made available by the vendor and can be integrated with just two function calls for bus read and write operations\footnote{IIS3DWB driver: \url{https://github.com/STMicroelectronics/iis3dwb-pid}}.

\subsection{Preliminary measurements}
% Describe preliminary measurements, waveform (1) orbital (2), velocity (3)

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
        \caption{Acceleration in $\mathrm{m/s}^2$}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
        \caption{Approximate velocity in $\mathrm{mm/s}$}
    \end{subfigure} 
    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
\end{figure}

% Velocity: integrated with composite trapezoidal rule and subtracted mean of envelope found by cubic interpolation of peaks.

% bandpass Butterworth filter of \nth{5} order with cuttoff frequencies f_{max} \pm 5 Hz.

\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
	\caption{Orbital analysis of compressor's 1x harmonic}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.54\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
        \caption{Spectral domain in x axis. FFT with Hann window of length $2^{10}$ ($\approx 409$ ms)}
    \end{subfigure} 
    \caption{Orbital and spectral methods of vibration signal analysis}
\end{figure}

% Historical logs of pump from KSB cloud

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{assets/design/ksb-cloud.jpg}
     \caption{KSB cloud pump monitoring after ramp up with displayed warning and alert levels}
\end{figure}
